---
title: "Plotly - an interactive plot tool in R"
author: "Suhas P K"
date: "2023-08-11"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Objective
- This project was created as part of the Developing Data Products course of the Coursera [Data Science Specialisation](https://www.coursera.org/specializations/jhu-data-science).

- The goal of the project is to create a web page presentation using R Markdown that features a plot created with Plotly, and to host the resulting web page on either GitHub Pages, RPubs, or NeoCities.

---

```{r libraries, echo=FALSE, message=FALSE}
if (!require(plotly)){
  install.packages("plotly")
  library(plotly)
}
```
- A classic diamond data set is used for this presentation.

- Here we will try to understand how prices of the diamond varies with the carat.

- Do note there are types of diamond cuts available.

- A simple scatter plot is enough to answer the above question.

---

The code is: 

```{r data, echo= TRUE, message=FALSE}

d <- diamonds[sample(nrow(diamonds), 1000), ]
fig <- plot_ly(
  d, x = ~carat, y = ~price,
  # Hover text:
  text = ~paste("Price: ", price, '$<br>Cut:', cut),
  color = ~cut, size = ~carat
)

```

---

```{r plot, warning=FALSE, message=FALSE}
fig
```


